---
title: "MATH4753.0231"
author: "Trey Hille"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753.0231)
```

# The MATH4753.0231 Package

This package contains several functions accumulated over the time spent completing the applied statistics course, MATH4753. It contains two sets of data as well as 8 functions. Of the 8 functions included, 6 return plots of various data, one returns a probability when given a negative binomial distribution, and one returns the working directory.

## Data Sets  

* This package contains two data sets:  

### ddt  
  * A data set collected by the US forces from the Tennessee River and its tributaries.  
  * Includes samples taken from three main rivers: FCM, LCM, and TRM.  
  * Samples from the rivers include three different species of fish; their length(cm), weight(g), and DDT content were recorded.  
```{r}
head(ddt)
```

### fire  
  * A data set which measures how far a fire originated from a fire station and how much damage the fire cause, in dollars.  
  * Includes two variables: The distance that a fire started from a fire station(miles) and the amount of damage done($1000) 
```{r}
head(fire)
```

## Non-Graphical Functions  

* This package contains two non-graphical functions: 

### mygetwd()

Returns the working directory.
```{r}
mygetwd()
```

### mynbin()

Returns the probability of the number of successes based on a negative binomial distribution.  
```{r}
mynbin(10, 3, 0.4)
```


## Graphical Functions  

* This package contains 6 functions that return plots:  

### myboot2()

Returns a histogram of the distribution of the sampled data from the population. On the histogram is a labeled confidence interval. 
```{r}
myboot2(iter = 10000, x = ddt$DDT, fun = "var", alpha = 0.2)
```

### myclt()

Returns a plot of the shape of the sample distribution taken randomly from a uniform distribution.  
```{r}
myclt(n = 20, iter = 100000, a = 0, b = 10)
```

### mymaxlikg()

Returns a graphical likelihood of a probability based on a supplied likelihood function. 
```{r}
mymaxlikg(lfun = "log", theta = seq(0,1,length=1000))
```

### myncurve()

Returns a plot and numerical value for the probability of a given number of successes for a normal distribution.  
```{r}
myncurve(10, 4, 3)
```

### scatterhist()

Returns a scatter plot histogram based on two given parameters and their respective labels.  
```{r}
scatterhist(ddt$LENGTH, ddt$WEIGHT, xlab = "Length", ylab = "Weight")
```

### myddt()

Returns a plot of the length vs. the weight of a given species, color coded by river. Also returns the entire data frame, the subsetted data frame, and a RIVER relative frequency table.  
```{r}
myddt(df = ddt, SPECIES = "CCATFISH")
```
